\setcounter{page}{1}
\section{Introduction}
Use this handout to follow along with the class. Each section contains some instructions and questions to be filled out.

At the start of the class, you will be given a test patient to work with.

\answer{Your test patient's MRN}

\section{Accession Numbers}

    \answermulti{How are the first 5 digits of an accession number defined?}

    \answer{What is a Container ID?}

\section{Department Order Entry}
This section is all about placing orders!

\activity{Set the default Values}\sideref{part:doe}{sec:doe_custom}

\activity{Change the Patient Identifier field to search for MRN}\sidenote{\hotkey{Ctrl+Tab}}

\activity{Search for your Patient using the MRN}\sideref{part:doe}{patientLookup}

\activity{Place an order for the following Tests:}
\begin{quote}
\begin{quote}
    \begin{itemize}
        \item Basic Metabolic Panel
        \item hCG Qualitative
        \item TNSIBC
        \item Chromosome Analysis on Bone Marrow
    \end{itemize}
\end{quote}
\end{quote}

\answer{Accession Number (Blood)}
\answer{Accession Number (Bone Marrow)}

\activity{Using a collect time in the future, order a CSF.}\sidenote{This will generate an ERROR.}
\begin{quote}
\begin{quote}
    \begin{itemize}
        \item CSFCT
    \end{itemize}
\end{quote}
\end{quote}

\activity{Fix the error, and re-submit the orders}

\answer{Accession Number (CSF)}

\subsection{Accession Add-On}

\activity{Add a PTT to the blood sample ordered earlier.}

\answer{Should you override?}

\section{Container Inquiry}

\activity{Search for your blood sample by accession number}

\answer{What is the \boldcap{In-Lab Location} of the PTT?}

\answer{What \boldcap{Service Resource} is it routed to?}

\section{Accession Result Entry}

This section is all about placing orders!

\activity{Set the Default Values}



\activity{Enter results for the BMPNL using the following criteria:}

\infoblock{Do not perform or validate these results.}

\begin{quote}
\begin{quote}
    \begin{itemize}
        \item Make at least \boldcap{Two} values critical.
        \item Make at least one value high.
        \item Make at least one value low.
        \item Make all results \boldcap{Within Linearity}
    \end{itemize}
\end{quote}
\end{quote}

\activity{Change the Sodium Result to 201}

\answer{What happened to the Anion Gap?}

\activity{Change the Chloride result to <50}

\answer{What happened to the Anion Gap?}

\activity{Convert the Anion Gap to an alpha response.}


\activity{Something}