\documentclass{exam}
\setlength\answerskip{0ex}
\setlength\answerlinelength{.8\textwidth}


\usepackage{fontspec}



% \newcommand{\fontset}{Lato}
\newcommand{\fontset}{SourceSansPro}
% \newcommand{\fontset}{Roboto}
% \newcommand{\fontset}{Delicious}
% \newcommand{\fontset}{FontinSans}
% \newcommand{\fontset}{ArchivoNarrow}
\newcommand{\fontfolder}{fonts/}

\newcommand{\boldface}{-Bold}
\newcommand{\italicface}{-Italic}
\newcommand{\regularface}{-Regular}
\newcommand{\bolditalicface}{-BoldItalic}
\newcommand{\smallcapface}{-SmallCaps}

\ifthenelse{\equal{\fontset}{SourceSansPro}}{
    \renewcommand{\boldface}{-Semibold}
    \renewcommand{\bolditalicface}{-SemiboldItalic}
}{}

\IfFileExists{\fontfolder\fontset/\fontset-Regular.ttf}{%
}{%
    \renewcommand{\fontfolder}{../fonts/}
}
\setmainfont{\fontset}[
    Path = \fontfolder\fontset/ ,
    UprightFont = *\regularface ,
    ItalicFont = *\italicface ,
    BoldFont = *\boldface ,
    BoldItalicFont = *\bolditalicface ,
    % SmallCapsFont = *\smallcapface,
  ]
\printanswers





\newcommand{\quest}[2]{
    \question #1
    \ifprintanswers
        \answerline[\textbf{#2}]
    \fi
    \fillwithlines{2\baselineskip}
}

\newcommand{\subquest}[2]{
    \part #1
    \ifprintanswers
        \answerline[\textbf{#2}]
    \fi
\fillwithlines{2\baselineskip}
}



\begin{document}

\section{Some Questions}
\begin{questions}

    \quest{Which application can simulate Power Charts?}{Order Result Viewer}

    \begin{parts}
        \subquest{What is the name of that mode?}{Flowsheet Mode}
    \end{parts}

    \quest{Which application is used to view the events of a collection?}{Container Inquiry}


    \quest{Which applications can be used to cancel orders?}{Pending Inquiry, Order result Viewer}

    \quest{Which application is used to view routing information on an order?}{Container Inquiry}

    \quest{Which application allows you to view Blood Bank Products?}{Patient Product Inquiry}

    \begin{parts}

    \subquest{How can you quickly branch to that application?}{Pending Inquiry}

    \end{parts}


    \quest{A result has been corrected, which application would you use to view the original result?}{Order Result Viewer}

    \question What \textsc{\textbf{Three}} hotkeys are needed to use comment templates?

        \begin{parts}
            \subquest{Hotkey 1}{F3}
            \subquest{What does it do?}{}
            \subquest{Hotkey 2}{F9}
            \subquest{What does it do?}{}
            \subquest{Hotkey 3}{F5}
            \subquest{What does it do?}{}
        \end{parts}

    \quest{What is the difference between a comment and a note?}{Note is lab only, comment is charted}









\end{questions}

\end{document}