\IfFileExists{bhrouting.tex}{\addcontentsline{toc}{chapter}{About Routing}}
\section{What is Routing?}

When Accession Numbers are assigned, Cerner will determine a \textsc{Service Resource}\sidenote{Testing location.} for the containers. The \textsc{Service Resource} is based on the \textsc{Procedure},\sidenote{\eg{CBC, Basic Panel, HbA\textsubscript{1c}, \etc}} \ and \textsc{Collection Location} of the container.


\newthought{This gives Cerner} the ability to update the status of a sample automatically based on the last place it was \textsc{Logged-in.}

\begin{quote}
    \boldcap{For example: } Let's say a CBC and a HbA\textsubscript{1c} are sent to \textsc{SMCA Laboratory}.

    When they're \textsc{Logged-in} to \textsc{SMC Login}, the CBC have an \textsc{In-Lab} status,\sidenote{Meaning, it's available to be tested.} while the HbA\textsubscript{1c} will have \textsc{Pending} status.\sidenote{Meaning, it's been collected but hasn't been sent yet.}
\end{quote}


\newthought{In addition to tracking,} the \textsc{Service Resources} is used in \gls{pi} as the \textsc{Test Site}.

\section{How Does It Work?}

\subsection{Instruments and Benches and Sections oh my!}

Every test is \boldcap{Routed} to either an \treeitem{instrument}{Instrument} or \treeitem{bench}{Bench}.\\

\treeitem{instrument}{Instruments} are interfaced instruments.\sidenote{They can send the results to Cerner.}

\treeitem{bench}{Benches} are where manual tests are performed.

 Since there are so many instruments\sidenote{We should start a band!} and benches we need a way to organize them. To do this we have \treeitem{section}{Sections} and \treeitem{subsection}{Subsections}.\\

 \treeitem{section}{Sections} are departments in the lab.\sidenote{Heme, Chem, UA, \etc}

 \treeitem{subsection}{Subsections} are areas of the sections.\sidenote{Manual Chemistry, Tegs, Miscellaneous Micro, \etc}


\subsection{All That To Say:}

Tests are routed to a \treeitem{bench}{Bench} or \treeitem{instrument}{Instrument}.

\noindent
\treeitem{bench}{Benches} and \treeitem{instrument}{Instruments} belong to a \treeitem{subsection}{Subsection}.

\noindent
\treeitem{subsection}{Subsections} belongs to a \treeitem{section}{Section}.

% \section{Example of Routing}
% {\setstretch{0.5}\scriptsize\scshape
%     \cfinput{../routing/smcrouting.tex}
% }

% This chapter contains a breakdown of the Seton Network Laboratories and their routing.

% \section{Instruments and Benches}

% Every test is \boldcap{Routed} to either an \instrument or \bench.\\

% \instruments are interfaced instruments.\sidenote{They can send the results to Cerner.}

% \benches are where manual tests are performed.

% \section{Sections and Subsections}

%  Since there are so many instruments\sidenote{We should start a band!} and benches we need a way to organize them. To do this we have \sects and \subsects.\\

% \sects are departments in the lab.\sidenote{Heme, Chem, UA, \etc}

% \subsects are areas of the sections.\sidenote{Manual Chemistry, Tegs, Miscellaneous Micro, \etc}


% \subsection{All That To Say:}

% Tests are routed to a \bench or \instrument.

% \noindent
% \benches and \instruments belong to a \subsect.

% \noindent
% \subsects belongs to a \sect.
% \clearpage


{\setstretch{0.5}\scriptsize\scshape
    \tikzset{
      dirtree/.style={
        growth function=\dirtree@growth,
        every node/.style={anchor=north},
        every child node/.style={anchor=west},
        edge from parent path={(\tikzparentnode\tikzparentanchor) |- (\tikzchildnode\tikzchildanchor)},
      }
    }

    \IfFileExists{bhrouting.tex}{%
        \addcontentsline{toc}{chapter}{Routing Maps}
        \cfsection{Brackenridge}{./}{bhrouting.tex}
        \cfsection{Dell Children's}{./}{dcrouting.tex}
        \cfsection{Edgar B. Davis}{./}{sebdrouting.tex}
        \cfsection{Hays}{./}{shcrouting.tex}
        \cfsection{Highland Lakes}{./}{shlrouting.tex}
        \cfsection{Northwest}{./}{snwrouting.tex}
        \cfsection{Southwest}{./}{sswrouting.tex}
        \cfsection{Williamson}{./}{swcrouting.tex}
        \cfsection{Seton Medical Center}{./}{smcrouting.tex}
    }{%
        \label{sec:routing_maps}
        \cfsection{Brackenridge}{../routing}{bhrouting.tex}
        \cfsection{Dell Children's}{../routing}{dcrouting.tex}
        \cfsection{Edgar B. Davis}{../routing}{sebdrouting.tex}
        \cfsection{Hays}{../routing}{shcrouting.tex}
        \cfsection{Highland Lakes}{../routing}{shlrouting.tex}
        \cfsection{Northwest}{../routing}{snwrouting.tex}
        \cfsection{Southwest}{../routing}{sswrouting.tex}
        \cfsection{Williamson}{../routing}{swcrouting.tex}
        \cfsection{Seton Medical Center}{../routing}{smcrouting.tex}
    }
}